On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-08-26 Manuscript/manuscript.tex
comments on styles and appendix

@@

% Place your title below. Use Title Capitalization.
\title{On Sample Size for Block Bootstrap Confidence Intervals 
  to Have Desired Coverage Rates}

@@

% Keywords are required.
\section*{keywords} 
List Eight to Ten Capitalized Keywords Separated by \ul{Semicolons}; Do Not Use Period at The End
Dependent Data; Resampling; Simulation; Time Series

@@

@@

@@

@@

>>>>

\usepackage{xcolor}
\newcommand{\jy}[1]{\textcolor{blue}{JY: #1}}
\newcommand{\eds}[1]{\textcolor{red}{EDS: (#1)}}
\newcommand{\mc}[1]{\textcolor{green}{MC: (#1)}}

@@

% Place your title below. Use Title Capitalization.
\title{On Sample Size Needed for Block Bootstrap Confidence Intervals
  to Have Desired Coverage Rates}

@@

% Keywords are required.
\section*{keywords} 
% List Eight to Ten Capitalized Keywords Separated by \ul{Semicolons}; Do Not Use Period at The End
Dependent Data; Resampling; Simulation; Time Series

@@

\jy{Are the results from exponential margins the same? If so, we can put them in
  an appendix; make sure we have the data generation process accurately
  described. Then briefly summarize and refer to it at the end of the simulation
  section.}

\jy{The 80-width is for maximum. No need to re-wrap shorter lines because it
  would show a lot of diff while there is no diff.}

@@

\jy{The fonts of labels/annotatios in these figures are too big compared to the
  captions. Try pointsize = 9. The plots also seem oversized. Generate them in R
  with the right size in mind.}

@@

\jy{Could do one for the exponential margin study too. Maybe for the negative dependence.}

@@

\appendix

\section{Simulation Study with Exponential Marginal Distribution}

\jy{Motivation; data generation (calibration of copula parameters to give the
  desired rho); simulation design; plots; brief discussion of results.}
